Models of lens candidates from Space Warps CFHTLS

### 2017-02-27 parts/app.tex
edits
editing

\subsection{Improved synthetic images}

@@

Figure~\figref{subsampling} shows an experiment with smaller mass
tiles in the inner region.  Replacing the very central mass tile with
9 smaller tiles allows for steeper central profiles.  Doing the same
for the 25 innermost mass tiles solves the problem completely, but
increases the number of mass tiles by 40\% and significantly increases
the computational time.
% 689 / 489 = 1.40899; in practice, runtime is more like x4 - x5!
% runtimes from logfiles: 87/22, 86/21, 85/16
The main modelling work in this paper was, however, done before the
experiments with smaller mass tiles was complete.  Some of the models
presented in this paper apply the intermediate option (corresponding
to the middle panel in Figure~\figref{subsampling}) while others use
the old system.  The results in this paper, however, mainly concern
the enclosed mass in the outer regions, so shallowness in the central
region should be inconsequential.

@@

Preliminary results on recovery of Einstein radii are shown in
Figure~\ref{fig:parameter}. \todo{Einstein radii from parametric
  model-fitting.}

\begin{figure}
  \includegraphics[width=\linewidth]{img/rE_comp/rE_comp.png}
  \caption{Comparison of Einstein radii. {\em To be extended.}}
  \label{fig:parameter}
\end{figure}

>>>>

\subsection{Improved synthetic images}\label{subsec:sourcefit}

@@

Figure~\figref{subsampling} shows an experiment with smaller mass
tiles in the inner region.  Replacing the very central mass tile with
9 smaller tiles allows for steeper central profiles.  Doing the same
for the 25 innermost mass tiles allows for still steeper central
profiles, eliminating the systematic shallowness.  This is, however,
still not a completely satisfactory solution, because (a)~it increases
the number of mass tiles by 40\% and significantly increases the
computational time, and (b)~the square boundary between area with
different tile sizes is rather undesirable.
% 689 / 489 = 1.40899; in practice, runtime is more like x4 - x5!
% runtimes from logfiles: 87/22, 86/21, 85/16
The main modelling work in this paper was, however, done before the
experiments with smaller mass tiles was complete.  Some of the models
presented in this paper apply the intermediate option (corresponding
to the middle panel in Figure~\figref{subsampling}) while others use
the old system.  The results in this paper, however, mainly concern
the enclosed mass in the outer regions, so shallowness in the central
region should be inconsequential.

@@

Preliminary results on recovery of Einstein radii are shown in
Figure~\ref{fig:parameter}. \todo{Einstein radii from parametric
  model-fitting for more candidates}

\begin{figure}
  \includegraphics[width=\linewidth]{img/rE_comp/rE_comp.png}
  \caption{Comparison of Einstein radii.}
  \label{fig:parameter}
\end{figure}
